The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-30 Writeup/paper_v3.tex
mention Euclid deep fields for ground-based survyes

\rachel{In contrast, for current and future ground-based surveys such
  as LSST, high-resolution space data will play a more important role
  in the understanding of the galaxy 
  intrinsic ellipticity and morphology distributions, since even a deep
  field in a ground-based survey faces fundamental resolution limits
  that prevent the derivation of detailed information about the faint
  galaxy population.  Galaxies that are near the resolution limit for
  a ground-based survey are still very well-resolved in {\em HST},
  making it the best resource for detailed information about them.}

>>>>

\rachel{In contrast, for current and future ground-based surveys such
  as LSST, high-resolution space data will play a more important role
  in the understanding of the galaxy 
  intrinsic ellipticity and morphology distributions, since even a deep
  field in a ground-based survey faces fundamental resolution limits
  that prevent the derivation of detailed information about the faint
  galaxy population.  Galaxies that are near the resolution limit for
  a ground-based survey are still very well-resolved in {\em HST},
  making it the best resource for detailed information about them.
  Once the Euclid deep field is publicly available, the information
  from it will be beneficial to ground-based surveys as well.}
